Draft Exploration

### 2020-04-13 draft_exploration.Rmd
added career peak distribution to shiny

@@

top_20_hs <- master %>%
  filter(source == "H" & draft_numb == 1) %>%
  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                             "<=College",
                             high_level)) %>%
  group_by(signed, high_level) %>%
  summarize(n = n()) %>%
  group_by(signed) %>%
  mutate(y = n/sum(n))

top_20_hs$high_level <- factor(top_20_hs$high_level,levels = c("<=College",
                                                               "Indy",
                                                               "Rk",
                                                               "A-",
                                                               "A",
                                                               "A+",
                                                               "AA",
                                                               "AAA",
                                                               "MLB"))

@@

peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 1)
```

>>>>

```{r, include=FALSE}
# PREPPING master data for peak level distribution in shiny by ordering
# high_level factors

master_peak <- master %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                                  "<=College",
                                  high_level)) %>%
  mutate(high_level = factor(high_level, levels = c("<=College",
                                                    "Indy",
                                                    "Rk",
                                                    "A-",
                                                    "A",
                                                    "A+",
                                                    "AA",
                                                    "AAA",
                                                    "MLB")))

@@

top_20_hs <- master %>%
  filter(source == "H" & draft_numb == 1) %>%
  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                             "<=College",
                             high_level)) %>%
  group_by(signed, high_level) %>%
  summarize(n = n()) %>%
  group_by(signed) %>%
  mutate(y = n/sum(n)) %>%
  mutate(high_level = factor(high_level,levels = c("<=College",
                                                   "Indy",
                                                   "Rk",
                                                   "A-",
                                                   "A",
                                                   "A+",
                                                   "AA",
                                                   "AAA",
                                                   "MLB")))

@@

peak_level(max_round = 20, startyear = 2010, endyear = 2010, min_round = 1)
```
